Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-05 Manuscript/manuscriptPS.tex
Update according to comments by M. Javanainen http://nmrlipids.blogspot.com/2018/12/nmrlipids-iv-toward-submission-of.html?showComment=1545138569759#c1540577296270662466

\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/NAdensPOPS.eps}
  \caption{\label{NAdensPOPS}
    Counterion densities of POPS lipid bilayer along the membrane normal from
    simulations with different force fields.
  }
\end{figure}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=18cm]{../Figs/CHANGESwithCaClPS.eps}
  \caption{\label{changesWITHCaClPS}
    Changes of POPC (left) and POPS (right) headgroup order parameters from POPC:POPS (5:1) mixture
    as a function CaCl$_2$ concentration from experiments \citenum{roux90} and different simulations
    at 298K (except the data for Berger model is from simulation of POPC:POPS (4:1) mixture at 310K \cite{ollila07a,melcrova16}). 
    The order parameter values from systems without calcium are set as the zero point of y-axis,
    except for the $\alpha$-carbon order parameter of POPS (bottom, right) for which the both order parameters are shifted
    such that the lower order parameter is zero without additional ions to correctly illustrate
    the forking with different concentrations of calcium.
    Potassium counterions are used in MacRog simulations and sodium counterions in Lipid14/17 simulations.
    In CHARMM36 and Berger simulation with added calcium, the charge is neutralized with calcium and monovalent counterions are not present.
  }
  \todo{Upcoming simulations with original CHARMM36 have been mentioned in the blog:
    http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1520090718976\#c5569269391707740056.
  these are not necessary, but could be added here if delivered.} \\
\end{figure*}

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
% Put your acknowledgments here.
  OHSO acknowledges financial support from Academy of Finland (315596),
  Integrated Structural Biology Research Infrastructure of
  Helsinki Institute of Life Science (Instruct-HiLIFE), and
  CSC-IT center for science for computational resources.
\end{acknowledgments}

>>>>

\begin{figure}[!htb]
  \centering
  \includegraphics[width=9.0cm]{../Figs/NAdensPOPS.eps}
  \caption{\label{NAdensPOPS}
    Counterion densities of POPS lipid bilayer along the membrane normal from
    simulations with different force fields.
  }
  \todo{Commented by M. Javanainen in blog:
    MacRog pure POPS is simulated with Verlet cutoff scheme, Piggot is rerunning with group cutoff scheme. Check if affects results \& update figures when ready}
\end{figure}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=18cm]{../Figs/CHANGESwithCaClPS.eps}
  \caption{\label{changesWITHCaClPS}
    Changes of POPC (left) and POPS (right) headgroup order parameters from POPC:POPS (5:1) mixture
    as a function CaCl$_2$ concentration from experiments \cite{roux90} and different simulations
    at 298K (except the data for Berger model is from simulation of POPC:POPS (4:1) mixture at 310K \cite{ollila07a,melcrova16}). 
    The order parameter values from systems without calcium are set as the zero point of y-axis,
    except for the $\alpha$-carbon order parameter of POPS (bottom, right) for which the both order parameters are shifted
    such that the lower order parameter is zero without additional ions to correctly illustrate
    the forking with different concentrations of calcium.
    Potassium counterions are used in MacRog simulations and sodium counterions in Lipid14/17 simulations.
    In CHARMM36 and Berger simulation with added calcium, the charge is neutralized with calcium and monovalent counterions are not present.
  }
  \todo{Upcoming simulations with original CHARMM36 have been mentioned in the blog:
    http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1520090718976\#c5569269391707740056.
  these are not necessary, but could be added here if delivered.} \\
\end{figure*}

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
% Put your acknowledgments here.
  OHSO acknowledges financial support from Academy of Finland (315596),
  Integrated Structural Biology Research Infrastructure of
  Helsinki Institute of Life Science (Instruct-HiLIFE), and
  CSC-IT center for science for computational resources.
  MJ acknowledges financial support from the Emil Aaltonen foundation and
  and CSC-IT center for science for computational resources.
\end{acknowledgments}

### 2019-02-05 Manuscript/manuscriptPSsuppl.tex
Update according to comments by M. Javanainen http://nmrlipids.blogspot.com/2018/12/nmrlipids-iv-toward-submission-of.html?showComment=1545138569759#c1540577296270662466

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/density_profile_CHARMM_CaCl_POPC_NBFix.pdf}
  \caption{\label{density_profile_CHARMM_CaCl_POPC_NBFix}
    Density profiles along membrane normal from CHARMM36 simulations with (middle)
    and without (top) the NBfix term for calcium \cite{kim16} compared to the simulation
    with the NBfix term for sodium \cite{venable13} (bottom). The simulation data are the same as in figure \ref{OP_CHARMM_CaCl_POPC_NBFix}.
  }
\end{figure}

\pagebreak
\section{Calcium density profiles from simulations with POPC:POPS(5:1) mixture}
\begin{figure}[ht]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixtureALL}
    Ca2+ density profiles from simulations.
  }
  \todo{Should we include also counterions into the plot?} \\
\end{figure}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=17.0cm]{../Figs/density_profile_CHARMM_CaCl_POPC_NBFix.pdf}
  \caption{\label{density_profile_CHARMM_CaCl_POPC_NBFix}
    Density profiles along membrane normal from CHARMM36 simulations with (middle)
    and without (top) the NBfix term for calcium \cite{kim16} compared to the simulation
    with the NBfix term for sodium \cite{venable13} (bottom). The simulation data are the same as in figure \ref{OP_CHARMM_CaCl_POPC_NBFix}.
  }
\end{figure}

\pagebreak
\section{Calcium density profiles from simulations with \\ POPC:POPS(5:1) mixture}
\begin{figure}[ht]
  \centering
  \includegraphics[width=10cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixtureALL}
    Ca2+ density profiles from simulations.
  }
  \todo{Should we include also counterions into the plot?} \\
\end{figure}
